Metrics

### 2023-11-19 src/metrics.Rmd
Finish pccc and csmf calcs and save to csv

@@

```{r}
pccc <- calc_by_age_stage(df, calc_pccc, "PCCC")
pccc
```

@@

```{r}
csmf_acc <- calc_by_age_stage(df, calc_csmf_acc, "CSMF Accuracy")
csmf_acc
```

>>>>

```{r}
metrics <- list()
```

@@

```{r}
metrics$pccc <- calc_by_age_stage(df, calc_pccc, "PCCC")
metrics$pccc
```

@@

```{r}
metrics$csmf_acc <- calc_by_age_stage(df, calc_csmf_acc, "CSMF Accuracy")
metrics$csmf_acc
```

## Results

Save calculated metrics to `data` folder.

```{r}
out <- reduce(metrics,
              function(x, y) left_join(x, y, by = "Model")
)
write_csv(out, "../data/healsl_rd1to2_metrics_v1.csv")
```
